Supplement to Automatic Matching of Bullet Lands

### 2016-11-30 imaging-paper.Rnw
Add bulletr references

library(RColorBrewer)
library(ggplot2)
library(scales)
library(dplyr)
library(x3pr)
library(x3prplus)
library(grid)
library(gridExtra)
library(zoo)
library(tidyr)
library(rpart)
library(rpart.plot)
library(xtable)
library(sm)
library(reshape2)
library(randomForest)
@

@@

br111 <- read.x3p(paste(datadir,"Br1 Bullet 1-5.x3p", sep = "/"))
dbr111 <- fortify_x3p(br111)

@@

#lof <- processBullets(paths = images[c(5,7)], x = 100)
subLOFx1 <- processBullets(read.x3p(images[5]), name = images[5], x = 100)
subLOFx2 <- processBullets(read.x3p(images[7]), name = images[7], x = 100)
#subLOFx1 <- subset(lof, bullet=="Br1 Bullet 1-5")
#subLOFx2 <- subset(lof, bullet=="Br1 Bullet 2-1")
subLOFx1$y <- subLOFx1$y + 23*1.5625 # working now!!!
lofX <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))

@@

#lof <- processBullets(paths = images[c(5,7)], x = 100)
subLOFx1 <- processBullets(read.x3p(images[5]), name = images[5], x = 100)
subLOFx2 <- processBullets(read.x3p(images[7]), name = images[7], x = 100)
#subLOFx1 <- subset(lof, bullet=="Br1 Bullet 1-5")
#subLOFx2 <- subset(lof, bullet=="Br1 Bullet 2-1")
subLOFx1$y <- subLOFx1$y - min(subLOFx1$y)
subLOFx2$y <- subLOFx2$y - min(subLOFx2$y)
ccf <- ccf(subLOFx1$resid, subLOFx2$resid, lag.max=100, plot=FALSE)
lag <- ccf$lag[which.max(ccf$acf)]
subLOFx1$y <- subLOFx1$y - lag*1.5625 
lofY <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))

@@

  subLOFx1 <- processBullets(read.x3p(images[5]), name = images[5], x = 100)
  subLOFx2 <- processBullets(read.x3p(images[7]), name = images[7], x = 100)
  lof <- rbind(subLOFx1, subLOFx2)

@@

crosscuts <- seq(100,250, by=25)
lof <- processBullets(read.x3p(paths[37]), name = paths[37], x = crosscuts)
lof$bullet <- paste(scrubPath(lof$bullet), lof$x)

@@

\section{Evaluation}
In order to get a better understanding of  how  the matching algorithm works in known matches and non-matches, we investigate its performance in a test scenario based on the James Hamby study.
As a first step, we automatically assess the quality of each of the lands by  checking that we can identify a stable region on each land. For this, we compute the cross-correlation of signatures extracted from heights 25$\mu m$ apart. For a stable region, we require a minimum of 0.95 for the cross correlation. Four lands from different bullets are flagged as problematic in this respect. A visual inspection (see Figure~\ref{fig:fourflags}) shows that each one of these lands has scratch marks across the surface, also known as `tank rash'.
%
\begin{figure}
  \centering
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 6 Bullet 2-1}
%' <<echo=FALSE>>=
%' b1 <- read.x3p(file.path(datadir, "Br6 Bullet 2-1.x3p"))
%' image(b1$surface.matrix)
%' @
\includegraphics[width=\textwidth]{images/br6-2-1-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 9 Bullet 2-4}
\includegraphics[width=\textwidth]{images/br9-2-4-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet B-2}
\includegraphics[width=\textwidth]{images/b-2-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet Q-4}
\includegraphics[width=\textwidth]{images/q-4-grey.png}
\end{subfigure}
\caption{\label{fig:fourflags}Images of the four lands that got flagged during the quality assessment. All of them show scratch marks (tank rash) across the striation marks from the barrel. They are excluded from the remainder of the analysis.}
\end{figure}
%
We exclude these four lands from further matching considerations and
 run all remaining lands from the unknown bullets against all remaining lands from known bullets for matches, i.e. we are comparing $15 \times 6 -2 = 90 - 2 = 88$ lands from unknown bullets against $2 \times 10 \times 6 -2 = 120 - 2 = 118$ lands from known bullets, yielding a total of $10,384$ land-to-land comparisons. Out of these comparisons, there are 172 known matches (KM), while the rest are known non-matches (KNM). 
 When things go well, they look like the results in Figure~\ref{fig:hamby-perfect}: Figure~\ref{fig:hamby-perfect}a shows the distribution of the number of maximum consecutive matching striae between land C-3 and all 118 lands from known bullets. Two lands show a high CMS. These correspond to the known matches with C-3, shown in Figures~\ref{fig:hamby-perfect}b and~\ref{fig:hamby-perfect}c. 
 Unfortunately, not all results are as clear cut. 
It might not be reasonable to assume that we can match all lands, but the idea is to try to maximize the number of matches to get an overview of what we might be able to expect from an automated match.

>>>>

library(RColorBrewer)
library(ggplot2)
library(scales)
library(dplyr)
library(bulletr)
library(grid)
library(gridExtra)
library(zoo)
library(tidyr)
library(rpart)
library(rpart.plot)
library(xtable)
library(sm)
library(reshape2)
library(randomForest)
@

@@

br111 <- read_x3p(paste(datadir,"Br1 Bullet 1-5.x3p", sep = "/"))
dbr111 <- fortify_x3p(br111)

@@

#lof <- processBullets(paths = images[c(5,7)], x = 100)
subLOFx1 <- processBullets(read_x3p(images[5]), name = images[5], x = 100)
subLOFx2 <- processBullets(read_x3p(images[7]), name = images[7], x = 100)
#subLOFx1 <- subset(lof, bullet=="Br1 Bullet 1-5")
#subLOFx2 <- subset(lof, bullet=="Br1 Bullet 2-1")
subLOFx1$y <- subLOFx1$y + 23*1.5625 # working now!!!
lofX <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))

@@

#lof <- processBullets(paths = images[c(5,7)], x = 100)
subLOFx1 <- processBullets(read_x3p(images[5]), name = images[5], x = 100)
subLOFx2 <- processBullets(read_x3p(images[7]), name = images[7], x = 100)
#subLOFx1 <- subset(lof, bullet=="Br1 Bullet 1-5")
#subLOFx2 <- subset(lof, bullet=="Br1 Bullet 2-1")
subLOFx1$y <- subLOFx1$y - min(subLOFx1$y)
subLOFx2$y <- subLOFx2$y - min(subLOFx2$y)
ccf <- ccf(subLOFx1$resid, subLOFx2$resid, lag.max=100, plot=FALSE)
lag <- ccf$lag[which.max(ccf$acf)]
subLOFx1$y <- subLOFx1$y - lag*1.5625 
lofY <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))

@@

  subLOFx1 <- processBullets(read_x3p(images[5]), name = images[5], x = 100)
  subLOFx2 <- processBullets(read_x3p(images[7]), name = images[7], x = 100)
  lof <- rbind(subLOFx1, subLOFx2)

@@

crosscuts <- seq(100,250, by=25)
lof <- processBullets(read_x3p(paths[37]), name = paths[37], x = crosscuts)
lof$bullet <- paste(scrubPath(lof$bullet), lof$x)

@@

\section{Evaluation}
In order to get a better understanding of  how  the matching algorithm works in known matches and non-matches, we investigate its performance in a test scenario based on the James Hamby study.
As a first step, we automatically assess the quality of each of the lands by  checking that we can identify a stable region on each land. For this, we compute the cross-correlation of signatures extracted from heights 25$\mu m$ apart. For a stable region, we require a minimum of 0.95 for the cross correlation. Four lands from different bullets are flagged as problematic in this respect. A visual inspection (see Figure~\ref{fig:fourflags}) shows that each one of these lands has scratch marks across the surface, also known as `tank rash'.
%
\begin{figure}
  \centering
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 6 Bullet 2-1}
%' <<echo=FALSE>>=
%' b1 <- read_x3p(file.path(datadir, "Br6 Bullet 2-1.x3p"))
%' image(b1$surface.matrix)
%' @
\includegraphics[width=\textwidth]{images/br6-2-1-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 9 Bullet 2-4}
\includegraphics[width=\textwidth]{images/br9-2-4-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet B-2}
\includegraphics[width=\textwidth]{images/b-2-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet Q-4}
\includegraphics[width=\textwidth]{images/q-4-grey.png}
\end{subfigure}
\caption{\label{fig:fourflags}Images of the four lands that got flagged during the quality assessment. All of them show scratch marks (tank rash) across the striation marks from the barrel. They are excluded from the remainder of the analysis.}
\end{figure}
%
We exclude these four lands from further matching considerations and
 run all remaining lands from the unknown bullets against all remaining lands from known bullets for matches, i.e. we are comparing $15 \times 6 -2 = 90 - 2 = 88$ lands from unknown bullets against $2 \times 10 \times 6 -2 = 120 - 2 = 118$ lands from known bullets, yielding a total of $10,384$ land-to-land comparisons. Out of these comparisons, there are 172 known matches (KM), while the rest are known non-matches (KNM). 
 When things go well, they look like the results in Figure~\ref{fig:hamby-perfect}: Figure~\ref{fig:hamby-perfect}a shows the distribution of the number of maximum consecutive matching striae between land C-3 and all 118 lands from known bullets. Two lands show a high CMS. These correspond to the known matches with C-3, shown in Figures~\ref{fig:hamby-perfect}b and~\ref{fig:hamby-perfect}c. 
 Unfortunately, not all results are as clear cut. 
It might not be reasonable to assume that we can match all lands, but the idea is to try to maximize the number of matches to get an overview of what we might be able to expect from an automated match.

### 2016-11-30 imaging-paper.tex
Add bulletr references

Each fired bullet is provided in the form of a set of six x3p files, where each file is a surface scan between adjacent grooves on the bullet, called a ``land". In the Hamby data, typical length (groove-to-groove) of a land is about 2005.9 micrometers or 2.01 millimeters. For notational simplicity, we refer to a particular land of some bullet as bullet X-Y, where X is the bullet identifier, and Y is the land number. An example of plotting one of these lands is given in Figures~\ref{fig:sidex3p} and~\ref{fig:topx3p}. These figures show side and top profiles of the land respectively. The tilt of the lines to the left in Figure~\ref{fig:topx3p} is not an artifact, but a direct and expected consequence of the spin induced by the rifling during the firing process. Depending on whether a barrel is rifled clockwise or counter-clockwise, the striations have a left or right tilt. The direction of the rifling is a class characteristic, i.e.\ a feature that pertains to a particular class of firearms, and is not unique at the individual barrel/bullet level.

@@

\subsection{Algorithm}\label{sec:algorithm}

\begin{figure}[hbtp]
\centering
    \begin{subfigure}[t]{\textwidth}\centering
\caption{Loess smooth of signatures  at a height of $x = 100\mu m$ (span is 0.03).\label{fig:smooth}}{%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=.65\textwidth]{figure/smooth-1}

\end{knitrout}
    }
\end{subfigure}
\begin{subfigure}[t]{\textwidth}\centering
\caption{Using a rolling median peaks and valleys are identified for each signature. Peaks and valleys on the signature correspond to striation marks on the bullet's surface. \label{fig:smoothcutb}}{%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=.65\textwidth]{figure/smoothcut-1}

@@

\begin{figure}[hbtp]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\textwidth]{figure/crosscuts-vary-b31-1}

\end{knitrout}
\caption{\label{fig:crosscuts2}Signatures  for barrel 3, bullet~1-1 extracted from varying heights. Initially, the match between signatures taken at heights 25$\mu m$ apart is affected strongly by some break off at the bottom of the bullet. At a  level of $175\mu m$ the bullet's signature stabilizes. For this land, matches should not be attempted at lower heights. }
\end{figure}
%An opportunity that arises from comparing multiple cross sections of a bullet's surface measurements is the following:

@@

\section{Evaluation}
In order to get a better understanding of  how  the matching algorithm works in known matches and non-matches, we investigate its performance in a test scenario based on the James Hamby study.
As a first step, we automatically assess the quality of each of the lands by  checking that we can identify a stable region on each land. For this, we compute the cross-correlation of signatures extracted from heights 25$\mu m$ apart. For a stable region, we require a minimum of 0.95 for the cross correlation. Four lands from different bullets are flagged as problematic in this respect. A visual inspection (see Figure~\ref{fig:fourflags}) shows that each one of these lands has scratch marks across the surface, also known as `tank rash'.
%
\begin{figure}
  \centering
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 6 Bullet 2-1}
%' <<echo=FALSE>>=
%' b1 <- read.x3p(file.path(datadir, "Br6 Bullet 2-1.x3p"))
%' image(b1$surface.matrix)
%' @
\includegraphics[width=\textwidth]{images/br6-2-1-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 9 Bullet 2-4}
\includegraphics[width=\textwidth]{images/br9-2-4-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet B-2}
\includegraphics[width=\textwidth]{images/b-2-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet Q-4}
\includegraphics[width=\textwidth]{images/q-4-grey.png}
\end{subfigure}
\caption{\label{fig:fourflags}Images of the four lands that got flagged during the quality assessment. All of them show scratch marks (tank rash) across the striation marks from the barrel. They are excluded from the remainder of the analysis.}
\end{figure}
%
We exclude these four lands from further matching considerations and
 run all remaining lands from the unknown bullets against all remaining lands from known bullets for matches, i.e. we are comparing $15 \times 6 -2 = 90 - 2 = 88$ lands from unknown bullets against $2 \times 10 \times 6 -2 = 120 - 2 = 118$ lands from known bullets, yielding a total of $10,384$ land-to-land comparisons. Out of these comparisons, there are 172 known matches (KM), while the rest are known non-matches (KNM). 
 When things go well, they look like the results in Figure~\ref{fig:hamby-perfect}: Figure~\ref{fig:hamby-perfect}a shows the distribution of the number of maximum consecutive matching striae between land C-3 and all 118 lands from known bullets. Two lands show a high CMS. These correspond to the known matches with C-3, shown in Figures~\ref{fig:hamby-perfect}b and~\ref{fig:hamby-perfect}c. 
 Unfortunately, not all results are as clear cut. 
It might not be reasonable to assume that we can match all lands, but the idea is to try to maximize the number of matches to get an overview of what we might be able to expect from an automated match.

\begin{figure}[hbtp]
\begin{subfigure}[t]{\textwidth}\centering
\caption{Maximal number of CMS between unknown bullet C-3 and all of the other 118 considered (known) lands. For two lands the number of maximum CMS is high. }
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=.5\textwidth]{figure/cms-1}

\end{knitrout}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{Overlaid signatures of C-3 and the land with the top matching CMS.}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\textwidth]{figure/top-1}

\end{knitrout}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{Top 2 match with C-3 based on CMS.}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\textwidth]{figure/top2-1}

\end{knitrout}
\end{subfigure}
\caption{\label{fig:hamby-perfect}Showcase scenario  when matching with CMS works very well. Unfortunately the matches are not always that convincing.}
\end{figure}

@@

\begin{figure}[hbtp]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=.65\textwidth]{figure/strange-res-1}

\end{knitrout}
\caption{\label{fig:mismatch}Known mismatch with a relatively large number of maximal consecutive matching striae (twelve) in the middle. The pattern in the middle does look surprisingly similar, however the outer ends of the signatures easily reveals this comparison as mismatch. }
\end{figure}

>>>>

Each fired bullet is provided in the form of a set of six x3p files, where each file is a surface scan between adjacent grooves on the bullet, called a ``land". In the Hamby data, typical length (groove-to-groove) of a land is about 1998.28 micrometers or 2 millimeters. For notational simplicity, we refer to a particular land of some bullet as bullet X-Y, where X is the bullet identifier, and Y is the land number. An example of plotting one of these lands is given in Figures~\ref{fig:sidex3p} and~\ref{fig:topx3p}. These figures show side and top profiles of the land respectively. The tilt of the lines to the left in Figure~\ref{fig:topx3p} is not an artifact, but a direct and expected consequence of the spin induced by the rifling during the firing process. Depending on whether a barrel is rifled clockwise or counter-clockwise, the striations have a left or right tilt. The direction of the rifling is a class characteristic, i.e.\ a feature that pertains to a particular class of firearms, and is not unique at the individual barrel/bullet level.

@@

\subsection{Algorithm}\label{sec:algorithm}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in 1:info\$num.pts.line: argument of length 0}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in 1:info\$num.pts.line: argument of length 0}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'subLOFx1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in data.frame(subLOFx1): object 'subLOFx1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'lofX' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'lofX' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in factor(lofX\$r05): object 'lofX' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in levels(lofX\$type) <- c("{}groove"{}, NA, "{}peak"{}): object 'lofX' not found}}\end{kframe}
\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'lofX' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in matches\$allnas: object of type 'closure' is not subsettable}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in matches\$allnas: object of type 'closure' is not subsettable}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}group\_by\_"{}): no applicable method for 'group\_by\_' applied to an object of class "{}function"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in subset.default(lines, lineid != 0): object 'lineid' not found}}\end{kframe}
\end{knitrout}

\begin{figure}[hbtp]
\centering
    \begin{subfigure}[t]{\textwidth}\centering
\caption{Loess smooth of signatures  at a height of $x = 100\mu m$ (span is 0.03).\label{fig:smooth}}{%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in strsplit(as.character(x), split = "{}/"{}): object 'lofX' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in ggplot(data, aesthetics, environment = env): object 'lofX' not found}}\end{kframe}
\end{knitrout}
    }
\end{subfigure}
\begin{subfigure}[t]{\textwidth}\centering
\caption{Using a rolling median peaks and valleys are identified for each signature. Peaks and valleys on the signature correspond to striation marks on the bullet's surface. \label{fig:smoothcutb}}{%
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=.65\textwidth]{figure/smoothcut-1}

@@

\begin{figure}[hbtp]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in 1:info\$num.pts.line: argument of length 0}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in strsplit(as.character(x), split = "{}/"{}): object 'lof' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in subset(lof, x \%in\% crosscuts[i:(i + 1)]): object 'lof' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in lapply(X = X, FUN = FUN, ...): object 'reslist' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in lapply(reslist, function(res) \{: object 'reslist' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in arrangeGrob(...): object 'lop' not found}}\end{kframe}
\end{knitrout}
\caption{\label{fig:crosscuts2}Signatures  for barrel 3, bullet~1-1 extracted from varying heights. Initially, the match between signatures taken at heights 25$\mu m$ apart is affected strongly by some break off at the bottom of the bullet. At a  level of $175\mu m$ the bullet's signature stabilizes. For this land, matches should not be attempted at lower heights. }
\end{figure}
%An opportunity that arises from comparing multiple cross sections of a bullet's surface measurements is the following:

@@

\section{Evaluation}
In order to get a better understanding of  how  the matching algorithm works in known matches and non-matches, we investigate its performance in a test scenario based on the James Hamby study.
As a first step, we automatically assess the quality of each of the lands by  checking that we can identify a stable region on each land. For this, we compute the cross-correlation of signatures extracted from heights 25$\mu m$ apart. For a stable region, we require a minimum of 0.95 for the cross correlation. Four lands from different bullets are flagged as problematic in this respect. A visual inspection (see Figure~\ref{fig:fourflags}) shows that each one of these lands has scratch marks across the surface, also known as `tank rash'.
%
\begin{figure}
  \centering
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 6 Bullet 2-1}
%' <<echo=FALSE>>=
%' b1 <- read_x3p(file.path(datadir, "Br6 Bullet 2-1.x3p"))
%' image(b1$surface.matrix)
%' @
\includegraphics[width=\textwidth]{images/br6-2-1-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 9 Bullet 2-4}
\includegraphics[width=\textwidth]{images/br9-2-4-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet B-2}
\includegraphics[width=\textwidth]{images/b-2-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet Q-4}
\includegraphics[width=\textwidth]{images/q-4-grey.png}
\end{subfigure}
\caption{\label{fig:fourflags}Images of the four lands that got flagged during the quality assessment. All of them show scratch marks (tank rash) across the striation marks from the barrel. They are excluded from the remainder of the analysis.}
\end{figure}
%
We exclude these four lands from further matching considerations and
 run all remaining lands from the unknown bullets against all remaining lands from known bullets for matches, i.e. we are comparing $15 \times 6 -2 = 90 - 2 = 88$ lands from unknown bullets against $2 \times 10 \times 6 -2 = 120 - 2 = 118$ lands from known bullets, yielding a total of $10,384$ land-to-land comparisons. Out of these comparisons, there are 172 known matches (KM), while the rest are known non-matches (KNM). 
 When things go well, they look like the results in Figure~\ref{fig:hamby-perfect}: Figure~\ref{fig:hamby-perfect}a shows the distribution of the number of maximum consecutive matching striae between land C-3 and all 118 lands from known bullets. Two lands show a high CMS. These correspond to the known matches with C-3, shown in Figures~\ref{fig:hamby-perfect}b and~\ref{fig:hamby-perfect}c. 
 Unfortunately, not all results are as clear cut. 
It might not be reasonable to assume that we can match all lands, but the idea is to try to maximize the number of matches to get an overview of what we might be able to expect from an automated match.

\begin{figure}[hbtp]
\begin{subfigure}[t]{\textwidth}\centering
\caption{Maximal number of CMS between unknown bullet C-3 and all of the other 118 considered (known) lands. For two lands the number of maximum CMS is high. }
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in readChar(con, 5L, useBytes = TRUE): cannot open compressed file 'data/data-25-25/unkn9.RData', probable reason 'No such file or directory'}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in lapply(X = X, FUN = FUN, ...): object 'reslist' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'cmsdist' not found}}\end{kframe}
\includegraphics[width=.5\textwidth]{figure/cms-1}

\end{knitrout}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{Overlaid signatures of C-3 and the land with the top matching CMS.}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'reslist' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in strsplit(as.character(x), split = "{}/"{}): object 'res' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in fortify(data): object 'res' not found}}\end{kframe}
\end{knitrout}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{Top 2 match with C-3 based on CMS.}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'reslist' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in strsplit(as.character(x), split = "{}/"{}): object 'res' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in fortify(data): object 'res' not found}}\end{kframe}
\end{knitrout}
\end{subfigure}
\caption{\label{fig:hamby-perfect}Showcase scenario  when matching with CMS works very well. Unfortunately the matches are not always that convincing.}
\end{figure}

@@

\begin{figure}[hbtp]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): object 'reslist' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in strsplit(as.character(x), split = "{}/"{}): object 'res' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in fortify(data): object 'res' not found}}\end{kframe}
\end{knitrout}
\caption{\label{fig:mismatch}Known mismatch with a relatively large number of maximal consecutive matching striae (twelve) in the middle. The pattern in the middle does look surprisingly similar, however the outer ends of the signatures easily reveals this comparison as mismatch. }
\end{figure}

### 2016-11-30 imaging-supplement.Rnw
Add bulletr references

library(RColorBrewer)
library(ggplot2)
library(scales)
library(dplyr)
library(x3pr)
library(x3prplus)
library(grid)
library(gridExtra)
library(zoo)
library(tidyr)
library(rpart)
library(rpart.plot)
library(xtable)
library(sm)
library(reshape2)
@

@@

<<bullet1, echo=FALSE, cache=TRUE>>=
db1 <- NULL
for (i in 1:6) {
  bname <- sprintf(file.path(datadir, "Br1 Bullet 1-%d.x3p"), i)
  dbi <- fortify_x3p(read.x3p(bname))
  dbi$part <- i
  db1 <- rbind(db1, dbi)
}

@@

<<bullet2, echo=FALSE, cache=TRUE>>=
db2 <- NULL
for (i in 1:6) {
  bname <- sprintf(file.path(datadir, "Br1 Bullet 2-%d.x3p"), i)
  dbi <- fortify_x3p(read.x3p(bname))
  dbi$part <- i
  db2 <- rbind(db2, dbi)
}

@@

crosscuts <- seq(100, 400, by = 50)
lof <- processBullets(read.x3p(paths[5]), name = scrubPath(paths[5]), x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

@@

\newpage
\section{Signature intensities}\label{supp:bulletbottom}
<<setup-signatures, echo=FALSE, message=FALSE>>=
library(x3pr)
library(x3prplus)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(zoo)

@@

# match unknown land using crosscuts
ccs <- read.csv("csvs/crosscuts-25-old.csv")
ccs$path <- file.path(knowndatadir, basename(as.character(ccs$path)))
all_bullets <- lapply(as.character(ccs$path), function(x) {
  result <- read.x3p(x)
  result[[3]] <- x
  names(result)[3] <- "path"

@@

  write.csv(stats, "csvs/crosscuts-sd.csv", row.names=FALSE)
} else {
  stats <- read.csv("csvs/crosscuts-sd.csv")
}
@
%
Figure~\ref{fig:overview} shows an overview of the signatures at different heights on a single bullet. 
\begin{figure}[hbtp]
<<one-bulletland-sd, echo=FALSE, dependson='setup-signatures', fig.height=5, fig.width=8, out.width='0.7\\textwidth', warning=FALSE>>=
k <- 1
x <- as.character(ccs$path)[k]
land <- read.x3p(x)
land[[3]] <- x
names(land)[3] <- "path"

>>>>

library(RColorBrewer)
library(ggplot2)
library(scales)
library(dplyr)
library(bulletr)
library(grid)
library(gridExtra)
library(zoo)
library(tidyr)
library(rpart)
library(rpart.plot)
library(xtable)
library(sm)
library(reshape2)
@

@@

<<bullet1, echo=FALSE, cache=TRUE>>=
db1 <- NULL
for (i in 1:6) {
  bname <- sprintf(file.path(datadir, "Br1 Bullet 1-%d.x3p"), i)
  dbi <- fortify_x3p(read_x3p(bname))
  dbi$part <- i
  db1 <- rbind(db1, dbi)
}

@@

<<bullet2, echo=FALSE, cache=TRUE>>=
db2 <- NULL
for (i in 1:6) {
  bname <- sprintf(file.path(datadir, "Br1 Bullet 2-%d.x3p"), i)
  dbi <- fortify_x3p(read_x3p(bname))
  dbi$part <- i
  db2 <- rbind(db2, dbi)
}

@@

crosscuts <- seq(100, 400, by = 50)
lof <- processBullets(read_x3p(paths[5]), name = scrubPath(paths[5]), x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

@@

\newpage
\section{Signature intensities}\label{supp:bulletbottom}
<<setup-signatures, echo=FALSE, message=FALSE>>=
library(bulletr)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(zoo)

@@

# match unknown land using crosscuts
ccs <- read.csv("csvs/crosscuts-25-old.csv")
ccs$path <- file.path(knowndatadir, basename(as.character(ccs$path)))
all_bullets <- lapply(as.character(ccs$path), function(x) {
  result <- read_x3p(x)
  result[[3]] <- x
  names(result)[3] <- "path"

@@

  write.csv(stats, "csvs/crosscuts-sd.csv", row.names=FALSE)
} else {
  stats <- read.csv("csvs/crosscuts-sd.csv")
}
@
%
Figure~\ref{fig:overview} shows an overview of the signatures at different heights on a single bullet. 
\begin{figure}[hbtp]
<<one-bulletland-sd, echo=FALSE, dependson='setup-signatures', fig.height=5, fig.width=8, out.width='0.7\\textwidth', warning=FALSE>>=
k <- 1
x <- as.character(ccs$path)[k]
land <- read_x3p(x)
land[[3]] <- x
names(land)[3] <- "path"
